---
title: "Performance Analysis at a Fixed Evaluation Budget"
output:
  bookdown::pdf_book:
    toc: false
documentclass: article
description: "Checkpoint fixed-budget performance supplementary material"
geometry: margin=1.5cm
params:
  model: "RF"
  evals: 500
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 9,
  fig.height = 6,
  out.width = "100%",
  fig.align = 'center')
```

```{r load-libraries, include=FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(kableExtra)
library(ggplot2)
```

```{r config, include=FALSE}
# The single model this report covers (override via render params::model).
MODEL <- params$model

# Hard-evaluation budget the strategies are compared at (override via
# render params::evals). Only checkpoints landing exactly on this many
# accumulated hard evaluations are used, so the value must sit on the run's
# checkpoint grid: Pop 25 checkpoints every 25 evals (25, 50, ..., 500) and
# Pop 50 every 50 (50, 100, ..., 500).
EVALS <- params$evals

# Performance metric analysed throughout this report.
METRIC <- "test_auc"
METRIC_LABEL <- "Test AUC"

# Search strategies, in exploration -> exploitation display order.
STRATEGY <- c("EA_Explore", "TPE25", "TPE50", "TPE75", "TPE100", "EA_Exploit")

# Colour-blind-friendly (Okabe-Ito) palette, one colour per strategy.
cb_palette <- setNames(
  c("#0072B2", "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7"),
  STRATEGY)

# Fillable point shapes (21-25 accept a fill), one per strategy.
SHAPE <- setNames(c(21, 22, 23, 24, 25, 21), STRATEGY)
```

```{r flat-violin, include=FALSE}
# Self-contained half ("flat") violin geom used for the raincloud plots below.
# Depends only on ggplot2 so the report knits without extra packages.
`%||%` <- function(a, b) if (!is.null(a)) a else b

GeomFlatViolin <- ggproto("GeomFlatViolin", Geom,
  setup_data = function(data, params) {
    data$width <- data$width %||% params$width %||%
      (resolution(data$x, FALSE) * 0.9)
    data$ymin <- ave(data$y, data$group, FUN = min)
    data$ymax <- ave(data$y, data$group, FUN = max)
    data$xmin <- data$x
    data$xmax <- data$x + data$width / 2
    data
  },
  draw_group = function(data, panel_scales, coord) {
    data <- transform(data, xminv = x, xmaxv = x + violinwidth * (xmax - x))
    ord <- order(data$y)
    newdata <- rbind(
      transform(data, x = xminv)[ord, ],
      transform(data, x = xmaxv)[rev(ord), ])
    newdata <- rbind(newdata, newdata[1, ])
    GeomPolygon$draw_panel(newdata, panel_scales, coord)
  },
  draw_key = draw_key_polygon,
  default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                    alpha = NA, linetype = "solid"),
  required_aes = c("x", "y"))

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomFlatViolin,
        position = position, show.legend = show.legend,
        inherit.aes = inherit.aes,
        params = list(trim = trim, scale = scale, ...))
}
```

```{r theme-setup, include=FALSE}
p_theme <- theme(
  plot.title = element_text(face = "bold", hjust = 0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  axis.title = element_text(size = 13),
  axis.text = element_text(size = 10),
  strip.text = element_text(size = 11, face = "bold"),
  axis.title.y = element_blank(),
  legend.position = "none",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)

# Raincloud plot of the fixed-budget metric by strategy, faceted by population
# size (rows) and mutation/variance (columns).
plot_performance <- function(data, title = NULL) {
  ggplot(data, aes(x = strategy, y = .data[[METRIC]],
                   color = strategy, fill = strategy, shape = strategy)) +
    geom_flat_violin(position = position_nudge(x = .1, y = 0),
                     scale = 'width', alpha = 0.2, width = 1.5) +
    geom_boxplot(color = 'black', width = .1, outlier.shape = NA,
                 alpha = 0.0, size = 0.6,
                 position = position_nudge(x = .16, y = 0)) +
    geom_point(position = position_jitter(width = 0.03, height = 0.0),
               size = 0.9, alpha = 0.8) +
    scale_y_continuous(name = METRIC_LABEL) +
    scale_x_discrete(name = "Strategy") +
    scale_shape_manual(values = SHAPE, limits = STRATEGY) +
    scale_colour_manual(values = cb_palette, limits = STRATEGY) +
    scale_fill_manual(values = cb_palette, limits = STRATEGY) +
    facet_grid(pop_label ~ mutvar_label) +
    ggtitle(title) +
    p_theme + coord_flip()
}
```

```{r helper-functions, include=FALSE}
# Five-number summary (min, Q1, median, Q3, max) of the metric per strategy,
# within one population-size / mutation-variance cell.
summarise_metric <- function(data, caption = NULL, label = NULL) {
  data %>%
    group_by(pop_label, mutvar_label, strategy) %>%
    summarise(
      min = min(.data[[METRIC]], na.rm = TRUE),
      Q1 = quantile(.data[[METRIC]], 0.25, na.rm = TRUE),
      median = median(.data[[METRIC]], na.rm = TRUE),
      Q3 = quantile(.data[[METRIC]], 0.75, na.rm = TRUE),
      max = max(.data[[METRIC]], na.rm = TRUE),
      .groups = "drop"
    ) %>%
    knitr::kable(format = "latex", booktabs = TRUE, digits = 4, longtable = TRUE,
                 col.names = c("Pop", "Mut/Var", "Strategy",
                               "Min", "Q1", "Median", "Q3", "Max"),
                 format.args = list(scientific = FALSE),
                 caption = caption, label = label) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"))
}

# Friedman test of the metric across strategies, blocking on seed, run
# independently within each population-size / mutation-variance cell. The test
# needs a complete block design, so seeds missing under any strategy in a cell
# are dropped; the number of complete blocks used is reported per cell.
friedman_table <- function(data, caption = NULL, label = NULL) {
  cells <- data %>% distinct(pop_label, mutvar_label)

  rows <- lapply(seq_len(nrow(cells)), function(i) {
    cell <- data %>%
      filter(pop_label == cells$pop_label[i],
             mutvar_label == cells$mutvar_label[i])

    wide <- cell %>%
      select(seed, strategy, dplyr::all_of(METRIC)) %>%
      tidyr::pivot_wider(names_from = strategy,
                         values_from = dplyr::all_of(METRIC))

    present <- intersect(STRATEGY, colnames(wide))
    mat <- as.matrix(wide[, present, drop = FALSE])
    mat <- mat[stats::complete.cases(mat), , drop = FALSE]

    # Friedman needs >= 2 strategies and >= 2 complete blocks.
    if (length(present) < 2 || nrow(mat) < 2) {
      return(data.frame(Pop = cells$pop_label[i],
                        MutVar = cells$mutvar_label[i],
                        Statistic = NA_real_, df = NA_integer_,
                        p.value = "NA", n_blocks = nrow(mat)))
    }

    res <- friedman.test(mat)
    p_value <- if (res$p.value < 1e-4) "$< 0.0001$" else
      formatC(res$p.value, format = "f", digits = 4)

    data.frame(Pop = cells$pop_label[i], MutVar = cells$mutvar_label[i],
               Statistic = round(unname(res$statistic), 3),
               df = unname(res$parameter), p.value = p_value,
               n_blocks = nrow(mat))
  })

  do.call(rbind, rows) %>%
    knitr::kable(format = "latex", booktabs = TRUE, digits = 4, longtable = TRUE,
                 col.names = c("Pop", "Mut/Var", "Friedman $\\chi^2$", "df",
                               "p-value", "Seeds (blocks)"),
                 escape = FALSE,
                 format.args = list(scientific = FALSE),
                 caption = caption, label = label) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"))
}
```

```{r load-data, include=FALSE}
data <- read.csv("checkpoint_trajectories.csv", header = TRUE,
                 stringsAsFactors = FALSE)

# Keep only this model's checkpoint at the requested budget: one row per run.
data <- data %>% filter(model == MODEL, hard_evals == EVALS)

if (nrow(data) == 0)
  stop(sprintf(
    "No %s checkpoints at hard_evals == %d. Pick a value on the checkpoint grid (Pop 25: 25, 50, ..., 500; Pop 50: 50, 100, ..., 500).",
    MODEL, EVALS))

data$strategy <- factor(data$strategy, levels = STRATEGY)
data$pop_label <- factor(sprintf("Pop %d", data$pop),
                         levels = sprintf("Pop %d", sort(unique(data$pop))))
data$mutvar_label <- factor(
  sprintf("mut=%.2f, var=%.2f", data$mut_rate, data$variance))
```

# Methodology

For model **`r MODEL`** we report the distribution of the **`r METRIC_LABEL`** of
the best-so-far individual after **`r EVALS`** accumulated hard evaluations,
across the `r length(STRATEGY)` search strategies
(`r paste(STRATEGY, collapse = ", ")`), and how that distribution shifts with the
two other experimental factors: population size (`r paste(levels(data$pop_label),
collapse = ", ")`) and the mutation/variance setting. Every configuration is
evaluated over 21 seeds.

For each task we present a raincloud plot of performance across strategies
(faceted by population size and mutation/variance), a five-number summary table,
and Friedman tests comparing strategies with observations paired by seed, run
separately within each population-size / mutation-variance cell. The Friedman
test requires a complete block design, so any seed missing under one or more
strategies in a cell is excluded; the number of complete seeds (blocks) used is
reported with each test.

```{r per-task, results='asis'}
tasks <- sort(unique(data$task))

for (task_id in tasks) {
  cat(sprintf("\n\n# %s\n\n", task_id))

  task_data <- filter(data, task == task_id)
  task_label <- gsub("_", "\\\\_", task_id)
  task_ref <- gsub("[^a-z0-9]+", "-", tolower(task_id))

  cat("\n\n")
  print(plot_performance(task_data,
                         title = sprintf("%s --- %s (model %s)",
                                         METRIC_LABEL, task_id, MODEL)))
  cat("\n\n")

  print(
    summarise_metric(task_data,
                     caption = sprintf("%s five-number summary --- %s",
                                       METRIC_LABEL, task_label),
                     label = sprintf("summary-%s", task_ref))
  )

  print(
    friedman_table(task_data,
                   caption = sprintf(
                     "Friedman test across strategies (paired by seed) --- %s",
                     task_label),
                   label = sprintf("friedman-%s", task_ref))
  )
}
```
