---
title: "Best-so-far Trajectory Analysis"
output:
  bookdown::pdf_book:
    toc: false
documentclass: article
description: "Checkpoint trajectory supplementary material"
geometry: margin=1.5cm
params:
  model: "RF"
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 4.5,
  out.width = "100%",
  fig.align = 'center',
  fig.pos = 'H')
```

```{r load-libraries, include=FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(ggplot2)
```

```{r config, include=FALSE}
# The single model this report covers (override via render params::model).
MODEL <- params$model

# Best-so-far metric tracked over accumulated hard evaluations.
METRIC <- "test_auc"
METRIC_LABEL <- "Test AUC (best-so-far)"

# Search strategies, in exploration -> exploitation display order.
STRATEGY <- c("EA_Explore", "TPE25", "TPE50", "TPE75", "TPE100", "EA_Exploit")

# Colour-blind-friendly (Okabe-Ito) palette, one colour per strategy.
cb_palette <- setNames(
  c("#0072B2", "#56B4E9", "#009E73", "#E69F00", "#D55E00", "#CC79A7"),
  STRATEGY)

# Fillable point shapes (21-25 accept a fill), one per strategy.
SHAPE <- setNames(c(21, 22, 23, 24, 25, 21), STRATEGY)
```

```{r theme-setup, include=FALSE}
p_theme <- theme(
  plot.title = element_text(face = "bold", hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  axis.title = element_text(size = 13),
  axis.text = element_text(size = 10),
  strip.text = element_text(size = 11, face = "bold"),
  legend.position = "bottom",
  legend.title = element_blank(),
  legend.text = element_text(size = 11),
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)

# Best-so-far trajectory for a single (task, population, mutation/variance)
# configuration: median across seeds with an inter-quartile ribbon, one line per
# strategy. One panel per figure -- no faceting.
plot_trajectory <- function(df, title = NULL, subtitle = NULL) {
  ggplot(df, aes(x = hard_evals, y = med,
                 color = strategy, fill = strategy, shape = strategy)) +
    geom_ribbon(aes(ymin = q1, ymax = q3), alpha = 0.15, colour = NA) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.0, colour = "black", stroke = 0.2) +
    scale_x_continuous(name = "Accumulated hard evaluations") +
    scale_y_continuous(name = METRIC_LABEL) +
    scale_colour_manual(values = cb_palette, limits = STRATEGY) +
    scale_fill_manual(values = cb_palette, limits = STRATEGY) +
    scale_shape_manual(values = SHAPE, limits = STRATEGY) +
    labs(title = title, subtitle = subtitle) +
    p_theme
}
```

```{r load-data, include=FALSE}
data <- read.csv("checkpoint_trajectories.csv", header = TRUE,
                 stringsAsFactors = FALSE)
data <- filter(data, model == MODEL)

# Ordered factors / readable facet labels.
data$strategy <- factor(data$strategy, levels = STRATEGY)
data$pop_label <- factor(sprintf("Pop %d", data$pop),
                         levels = sprintf("Pop %d", sort(unique(data$pop))))
data$mutvar_label <- factor(
  sprintf("mut=%.2f, var=%.2f", data$mut_rate, data$variance))

# Median + inter-quartile band of the metric across the 21 seeds, per
# (pop, mut/var, strategy, task, hard_evals) cell.
traj <- data %>%
  group_by(pop, pop_label, mut_rate, variance, mutvar_label,
           strategy, task, hard_evals) %>%
  summarise(
    med = median(.data[[METRIC]], na.rm = TRUE),
    q1  = quantile(.data[[METRIC]], 0.25, na.rm = TRUE),
    q3  = quantile(.data[[METRIC]], 0.75, na.rm = TRUE),
    n   = dplyr::n(),
    .groups = "drop")
```

# Methodology

This report tracks how the **`r METRIC_LABEL`** of the best-so-far individual
evolves over the shared 500 hard-evaluation budget for model **`r MODEL`**. Each
line is the median across 21 seeds and the shaded band spans the inter-quartile
range (Q1--Q3). Lines are coloured by search strategy
(`r paste(STRATEGY, collapse = ", ")`).

Because a generation costs one population's worth of evaluations, population size
sets how finely the budget is sampled: `Pop 25` checkpoints every 25 evaluations
(20 points), `Pop 50` every 50 (10 points). A separate single-panel figure is
produced for every (task, population size, mutation/variance) configuration, so
each population keeps its own `hard_evals` grid and no cross-population
interpolation is performed.

```{r per-config, results='asis'}
tasks   <- sort(unique(traj$task))
pops    <- levels(traj$pop_label)
mutvars <- levels(traj$mutvar_label)

for (task_id in tasks) {
  cat(sprintf("\n\n# %s\n\n", task_id))

  for (pop in pops) {
    for (mv in mutvars) {
      # Use the .env pronoun so the loop variables are not shadowed by the
      # same-named data columns (e.g. traj$pop) under dplyr data-masking.
      cfg <- traj %>%
        filter(task == .env$task_id,
               pop_label == .env$pop,
               mutvar_label == .env$mv)
      if (nrow(cfg) == 0) next

      cat(sprintf("\n\n## %s --- %s, %s\n\n", task_id, pop, mv))
      cat("\n\n")
      print(plot_trajectory(
        cfg,
        title = sprintf("%s --- %s (model %s)", METRIC_LABEL, task_id, MODEL),
        subtitle = sprintf("%s, %s", pop, mv)))
      cat("\n\n")
    }
  }
}
```
